---
title: "Final Report"
author: "Sara Baji"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

This project uses the AI in Healthcare dataset which contains 5,000 patient records with 20 variables capturing demographic, clinical, and AI-related information.   
The purpose is to explore whether the AI model’s confidence relates to recovery time and satisfaction. I use summary statistics and a simple scatterplot to 
look for any clear patterns.

# Data
```{r setup, include=FALSE}

library(tidyverse)
library(janitor)
library(knitr)

source("code/utils.R")
source("code/01_load_and_clean.R")

```

```{r data_overview, echo=FALSE, results='asis'}
# Show dataset shape as text
cat("**Number of rows:**", nrow(dat), "<br>")
cat("**Number of columns:**", ncol(dat), "<br><br>")

# Display first few rows nicely
knitr::kable(head(dat), caption = "Preview of the AI in Healthcare Dataset")
```

# Table
```{r table1, message=FALSE, warning=FALSE, echo=FALSE}
# make sure the table exists
source("code/02_make_table1.R")

# read and display table 1 nicely
tab_path <- "tables/table1_summary.csv"
if (file.exists(tab_path)) {
  tab1 <- readr::read_csv(tab_path, show_col_types = FALSE)
  knitr::kable(tab1, caption = "Summary statistics")
} else {
  stop("table not found at: ", tab_path)
}
```

# Figure
```{r figure1, message=FALSE, warning=FALSE, echo=FALSE}
# make sure the figure exists
source("code/03_make_fig1.R")

# include the figure
fig_path <- "figs/fig_ai_vs_recovery.png"
if (file.exists(fig_path)) {
  knitr::include_graphics(fig_path)
} else {
  stop("figure not found at: ", fig_path)
}
```

*Note:* I am checking whether higher AI confidence is linked to
shorter recovery time. This is only a descriptive analysis, so it does not
prove causation.